\documentclass[a4paper,11pt]{article}

% Packages
\usepackage[utf8]{inputenc}
\usepackage{amsmath, amssymb}
\usepackage{graphicx}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{float}
\usepackage{authblk} % For author affiliations
\usepackage{caption}
\usepackage{subcaption}
\usepackage{cite}

% Geometry settings
\geometry{margin=1in}

% Title Information
\title{Spatial Ecology of Territorial Populations: Modeling and Analysis}
\author[1]{Jacopo Carotenuto}
\affil[1]{University of Padova, Physics of Data}
\date{\today}

\begin{document}

\maketitle

\begin{abstract}
\textbf{WRITTEN BY CHATGPT REWRITE}
This study investigates the impact of spatial structure and metabolic trade-offs on biodiversity in ecosystems with territorial populations. Using a 1D spatial model with nutrient diffusion and trade-offs, we analyze the dynamics of resource competition, population stability, and emergent ecological effects such as the Allee effect and multistability. Our findings highlight the roles of nutrient diffusion and oligotroph dominance in shaping biodiversity and propose extensions for more complex ecosystems.
\end{abstract}

\section{Introduction}
Introduce the topic, including the importance of spatial ecology, resource competition, and biodiversity. Summarize the main contributions of this study and outline the paper's structure.

\section{Model Description}
\subsection{Mathematical Framework}
Describe the model, including:
\begin{itemize}
    \item Spatial structure (1D domain with periodic boundaries).
    \item Nutrient diffusion dynamics.
    \item Population dynamics and metabolic trade-offs.
\end{itemize}

\subsection{Parameter Definitions}
Provide definitions and notations for parameters such as diffusion coefficient, nutrient supply rate, and enzyme budgets.

\section{Results and Discussion}
\subsection{Biodiversity in Spatial Communities}
Present findings on how spatial structure influences biodiversity compared to well-mixed systems.

\subsection{Oligotroph Dominance and Extinctions}
Analyze the role of oligotrophs in reducing diversity and compare outcomes under varying nutrient supply conditions.

\subsection{Stability and Dynamics}
Discuss emergent phenomena like multistability, slow population dynamics, and the Allee effect.

\section{Methods}
\subsection{Numerical Implementation}
Detail the numerical methods used, such as solvers and parameters for simulations.

\subsection{Validation and Sensitivity Analysis}
Explain how the model was validated and its sensitivity to key parameters.

\section{Conclusion and Future Work}
Summarize the main findings and propose extensions, such as higher-dimensional models or stochastic dynamics.

\section*{References}
\bibliographystyle{plain}
\bibliography{references} % Create a references.bib file for citations.

\end{document}